The problem and promise of scale in animal social multilayer networks

### 2020-02-09 paper/manuscript.Rmd
P2 movement persp

<!-- remove italics from terms? -->
Although multilayer animal social networks are relatively novel (Silk et al.
2018), movement behaviour within multilayer networks has already been considered
in a couple studies. In vulturine gunieafowl (*Acryllium vulturinum*), GPS
movement data were used to generate *monolayer* association networks within a
multilayer network (Papageorgiou et al. 2019). In addition, *spatial networks*
are physical locations (nodes) which are connected in a network when individuals
move between said locations (edges). For example, spatial networks were applied
to monitor movement of sharks (*Carcharhinus amblyrhynchos* and *Carcharhinus
melanopterus*) between fixed location autonomous arrays. In this example, nodes
represent locations within the array, *intralayer edges* represent individual
movement frequency, and *interlayer edges* represent contact probability among
individuals at a given node (Mourier et al. 2019). While both studies integrate
movement in some capacity, neither generate networks based on continuous
measures of dyadic or collective movement (Long et al. 2014).

>>>>

Although multilayer animal social networks are relatively novel (Silk et al.
2018), movement behaviour within multilayer networks has been considered.  Spatial
networks are physical locations (nodes) which are connected in a network when individuals
move between said locations (edges). For example, spatial networks were applied
to monitor movement of sharks (*Carcharhinus amblyrhynchos* and *Carcharhinus
melanopterus*) between fixed location autonomous arrays. In this example, nodes
represent locations within the array, *intralayer edges* represent individual
movement frequency, and *interlayer edges* represent contact probability among
individuals at a given node (Mourier et al. 2019). Although movement between 
fixed arrays is inherent, networks are not constructed based on continuous 
measures of dyadic or collective movement (Long et al. 2014). Our case study 
builds on the work of Mourier et al. (2019) and explicitly integrates 
continuous and simultaneous measures of animal movement through space 
and time as layers of a multilayer social network.
